A Privacy Aware Mobile Sensor Application

### 2015-02-05 paper.tex
privacy recommendation changed

\textbf{Privacy Dashboard (R1)}. In order to address the threat with the highers risk, Insufficient Control (T1) of the citizen, we need to give the citizen back the
control over its data inside the system. The most direct way to do
this is to provide a web-based overview which allows the citizen to view, edit and delete all information about his person
that is stored inside the system.

\textbf{Privacy Policy (R2)}. A necessary pre-requirement for effective control of the citizen over his data is information and comprehension of the intended data capturing and processing steps. Therefore a policy that
is easily readable and contains all important information is essential and a legal requirement.

\textbf{Data Handling Guidelines (R3)} The threat with the second largest risk is (T2) Excessive Data Mining.
Contrary to common belief, it is neither legal nor ethical to process
personal data for by new methods or for new purposes that were not
stated and explained to the citizen at the time of data
collection. Also the common practice of obtaining far-reaching
permissions from the citizens inside the privacy policy is neither an
ethical or legal solution to the problem. To address this threat awareness about the limitations of data
processors inside the company is a key element. As one mean to
establish such a culture of privacy respect, we recommend to prepare
an guideline intended for internal use that explains the concrete processing steps and purposes that are permitted by the citizens.

\textbf{User Permissions (R4)}. If further processing should be performed, it is necessary to seek additional permissions from the citizen. A simple email explaining the planned processing steps, and asking for permissions would be enough for this purpose. The permission can be given via an embedded link that shall be followed in order to signal agreement.

\textbf{Anonymization (R5)} An alternative measure to address the risk of excessive data mining is the anonymization of data. When all direct- or indirect
links to the identity of the person are removed, no violation of the
citizens privacy caused by arbitrary processing. However removing all
such links is a challenging tasks, and full anonymity is often not
achieved, cf. \cite{krumm2009}.

\textbf{IT Infrastructure Security (R6)}. The protection from threat scenario (T3) Data Theft is a case of
classical IT infrastructure security. The storage and processing infrastructure has
to be secured using firewalls, up-to data software versions and proper
authentication mechanisms.

\textbf{Encryption (R7)} The protection from threat scenario (T4) Surveillance focuses on the
communication channels. They are target of wiretapping attacks by
intermediaries or externals with access to the communication
infrastructure. Strong encryption should be used to make
it harder for externals to read the content of the transmitted data.

\textbf{Relationship (R8)}. Threat scenarios (T5) Information Leak and (T6) Social Engineering
target the vulnerability of unhappy employees. Therefore a trustful,
healthy company culture should be maintained.

>>>>

\textbf{R1. Privacy Dashboard}. In order to address the threat with the highers risk, Insufficient Control (T1) of the citizen, we need to give the citizen back the
control over its data inside the system. The most direct way to do
this is to provide a web-based overview which allows the citizen to view, edit and delete all information about his person
that is stored inside the system.

\textbf{R2. Privacy Policy}. A necessary pre-requirement for effective control of the citizen over his data is information and comprehension of the intended data capturing and processing steps. Therefore a policy that
is easily readable and contains all important information is essential and a legal requirement.

\textbf{R3. Data Handling Guidelines}. The threat with the second largest risk is (T2) Excessive Data Mining.
Contrary to common belief, it is neither legal nor ethical to process
personal data for by new methods or for new purposes that were not
stated and explained to the citizen at the time of data
collection. Also the common practice of obtaining far-reaching
permissions from the citizens inside the privacy policy is neither an
ethical or legal solution to the problem. To address this threat awareness about the limitations of data
processors inside the company is a key element. As one mean to
establish such a culture of privacy respect, we recommend to prepare
an guideline intended for internal use that explains the concrete processing steps and purposes that are permitted by the citizens.

\textbf{R4. User Permissions}. If further processing should be performed, it is necessary to seek additional permissions from the citizen. A simple email explaining the planned processing steps, and asking for permissions would be enough for this purpose. The permission can be given via an embedded link that shall be followed in order to signal agreement.

\textbf{R5. Anonymization}. An alternative measure to address the risk of excessive data mining is the anonymization of data. When all direct- or indirect
links to the identity of the person are removed, no violation of the
citizens privacy caused by arbitrary processing. However removing all
such links is a challenging tasks, and full anonymity is often not
achieved, cf. \cite{krumm2009}.

\textbf{R6. IT Infrastructure Security}. The protection from threat scenario (T3) Data Theft is a case of
classical IT infrastructure security. The storage and processing infrastructure has
to be secured using firewalls, up-to data software versions and proper
authentication mechanisms.

\textbf{R7. Encryption}. The protection from threat scenario (T4) Surveillance focuses on the
communication channels. They are target of wiretapping attacks by
intermediaries or externals with access to the communication
infrastructure. Strong encryption should be used to make
it harder for externals to read the content of the transmitted data.

\textbf{R8. Relationship}. Threat scenarios (T5) Information Leak and (T6) Social Engineering
target the vulnerability of unhappy employees. Therefore a trustful,
healthy company culture should be maintained.
